Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-01 latex/robdml.tex
tex

\textbf{Adversarial Attack.}
%
Szegedy \etal~\cite{l-bfgs} find misclassification of DNN can be triggered by
an imperceptible adversarial perturbation to the input image.
%
Ian \etal~\cite{fgsm} speculate the reason is that DNN being locally linear
with respect to the adversarial perturbation.
%
A series of following works attempt to more efficiently compromise the DNNs,
such as BIM~\cite{i-fgsm}, C\&W~\cite{cw}, PGD~\cite{madry}, and
APGD~\cite{apgd}.
%
These attacks are based on the first-order gradient of the classification loss
with respect to the input image, and hence rely on the white-box assumption
that the model architecture and parameters are accessible to the attacker,
which is impractical for real-world attacks.
%
Subsequently, black-box attack methods are developed into two types:
transferrability-based attacks and query-based attacks.
%
Transferrability-based attacks relies on the observation that image-agnostic
(will take effect when applied to any image) and model-agnostic (will take
effect when applied to any model) adversarial perturbation are possible.
%
Query-based attacks only need the logit score output or the label output from a
classifier, based on which the gradient could be estimated from the response to
repetitive queries in order to figure out the adversarial perturbation.

\textbf{Adversarial Defense.}
%
To battle against the attacks, some early defense
methods create a gradient masking effect, namely making it hard for the attacker
to find a good gradient, but it gives a false sense of security~\cite{obfuscated}.
%
Defensive distillation~[] can be compromised by C\&W~\cite{cw}.
%
Ensemble of weak defenses is insufficient~[].
%
Defense can also be implemented as preprocessing~[] or reconstructing~[] the input
image, or a randomized process inside the network~[].
%
However, it is noted that various defense methods are still susceptible to
adaptive attack~\cite{adaptive}.
%
Among the proposed defense methods, adversarial training has been empirically
found effective~[][], and it consistently retains adversarial robustness
for the model.

>>>>

\textbf{Adversarial Attack.}
%
Szegedy \etal~\cite{l-bfgs} find misclassification of DNN can be triggered by
an imperceptible adversarial perturbation to the input image.
%
Ian \etal~\cite{fgsm} speculate the reason is that DNN being locally linear
with respect to the adversarial perturbation.
%
A series of following works attempt to more efficiently compromise the DNNs,
such as BIM~\cite{i-fgsm}, C\&W~\cite{cw}, PGD~\cite{madry}, and
APGD~\cite{apgd}.
%
These attacks are based on the first-order gradient of the classification loss
with respect to the input image, and hence rely on the white-box assumption
that the model architecture and parameters are accessible to the attacker,
which is impractical for real-world attacks.
%
Subsequently, black-box attack methods are developed into two types:
transferrability-based attacks and query-based attacks.
%
Transferrability-based attacks~\cite{di-fgsm,universal} relies on the observation that image-agnostic
(will take effect when applied to any image) and model-agnostic (will take
effect when applied to any model) adversarial perturbation are possible.
%
Query-based attacks~\cite{nes-atk,spsa-atk} only need the logit score output or the label output from a
classifier, based on which the gradient could be estimated from the response to
repetitive queries in order to figure out the adversarial perturbation.

\textbf{Adversarial Defense.}
%
To battle against the attacks, some early defense
methods create a gradient masking effect, namely making it hard for the attacker
to find a good gradient, but it gives a false sense of security~\cite{obfuscated}.
%
Defensive distillation~\cite{distill2} can be compromised by C\&W~\cite{cw}.
%
Ensemble of weak defenses is insufficient~\cite{ensembleweak}.
%
Defense can also be implemented as preprocessing~\cite{deflecting} the input
image, or a randomized process inside the network~\cite{self-ensemble}.
%
However, it is noted that various defense methods are still susceptible to
adaptive attack~\cite{adaptive}.
%
Among the proposed defense methods, adversarial training has been empirically
found effective~\cite{bilateral,advtrain-triplet,benchmarking}, and it consistently retains adversarial robustness
for the model.
